\section{Introduction}
\label{sec:introduction}
Neural networks experienced a steep rise in popularity over the last years. One reason for this trend is the versatility of these networks. They are being deployed in many domains such as computer vision and pattern recognition, predictions, robotics and self-driving cars and many more. 
\\
However, quite few scientific papers of neural networks are released in the financial domain with the objective to predict the development of stock prices. 
%The reason for this might be controversial as the ability to predict stock course development approximately may result in exploitation. This papers motivation, however, is scientifically. 
% volatile and shit
The task of stock course prediction is difficult as the stock prices are influenced by a multitude of seemingly unpredictable and uncorrelated factors. Nevertheless, the development of a stock course depends strongly on the actions of traders. Those traders could use the search engine google to gather information about stocks they are interested in right before a trade. The service \textit{Google Trends} views various graphs displaying data of search terms typed in by users at the google search engine. This service is accessible by the public. Based on these thoughts the following hypothesis can be formulated: 
\\
\textit{A correlation between google trends search terms and stock courses exists. } 
\\
In this paper the previous hypothesis is being investigated. In order to check the existence of a correlation between goolge trends data and stock courses, a neural network will be implemented and verified. 
\\ \\
TODO: bei den related work papern schauen, ob hier material für weiteres zum Intro passen würde!!!
\\